---
title: "Notes on calculating objectives"
author: "Peter Baker"
date: "Thursday 5 February 2015"
output:
html_document:
  toc: true
  theme: united
pdf_document:
  toc: true
  highlight: zenburn
---

```{r}
##library(rstudio)
library(knitr)
library(rmarkdown)
library(pander)
library(lubridate)
```

# Introduction

**R**, *STATA*, __SPSS__, _SAS_ and most other statistical and database packages
access data via variable names. These names don't include spaces
because this would make programming very difficult indeed.  As such,
variable names aren't very nice to look at when printing tables or
producing plots. Most packages therefore provide a way of labelling
variables when producing output. While these variable labels are
called different things in most packages these are linked to variable
names without user intervention.

REDCAP provides a .csv file and .R (or stata) file that can be
employed YO YO


# Demo of simple R

```{r foo, echo = TRUE}
sessionInfo()
z <- 1+1
```

z is `r z`

emacs polymode doesn't play well with .Rnw syntax but this should
still work but doesn't seem to do so'. 

```{r bar}
hist(rnorm(1000))
```
