---
title: "Example Routine Project"
author: "Peter Baker"
date: "Wed Oct 26 17:17:52 2016"
output:
  html_document:
    toc: true
    theme: united
  pdf_document:
    toc: true
    highlight: zenburn
---

Results of simple linear regression

```{r, echo=FALSE, messages=FALSE, warnings=FALSE, errors=TRUE}
suppressMessages(library(knitr))
suppressMessages(library(rmarkdown))
suppressMessages(library(pander))
suppressMessages(library(RcmdrMisc))
suppressMessages(library(effects))

load(file.path("../data/derived", "clean_simple_csv.RData"))
load(file.path("../data/derived", "analyse_simple_csv.RData"))
```

# Statistical Analysis

Simple  *R* and output:
```{r}
summary(lm1)
```

Nicer versions can be printed using *pander*.

```{r, echo=FALSE, results='asis'}
  pander(summary(lm1))
```

And ANOVAs
  
```{r, echo=FALSE, results='asis'}
if (exists("lm1")) {
  knitr::kable(anova(lm1))
  knitr::kable(Anova(lm1))
}
```

And perhaps some standard residual plots.

```{r, echo=FALSE, hold = TRUE, fig.cap = "Standard Residual Plots"}
opPars <- par(mfrow = c(2, 2), oma = c(0, 0, 2, 0))
plot(lm1)
par(opPars)
```

Residual plots using *car* package.

```{r, echo=FALSE, fig.cap = "CAR Residual Plots"}
if (exists("lm1")) car::residualPlots(lm1)
```

And can plot effects stored previously

```{r, echo=FALSE, fig.cap = "Effects Plot using library(effects)"}
  plot(allEff1)
```

The slope was `r round(coef(lm1)[2], 2)` with se `r round(coef(summary(lm1))['x', 'Std. Error'], 2)` and p-value `r format.pval(coef(summary(lm1))['x', 4], eps = 0.001)`.
