---
title: "Summary statistics for 'simple.csv'"
author: Peter Baker 
date: "Wed Oct 26 17:17:52 2016"
output:
  html_document:
    toc: true
    theme: united
  pdf_document:
    toc: true
    highlight: zenburn
---

This is a possible report to summarise the data file *simple.csv*.

```{r, echo=FALSE, messages=FALSE, warnings=FALSE, errors=TRUE}
library(knitr)
library(rmarkdown)
library(pander)
library(RcmdrMisc)

load(file.path("../data/derived", "clean_simple_csv.RData"))
load(file.path("../data/derived", "summary_simple_csv.RData"))
N.CASES <- dim(clean_data)[1]
```

# Summary Statistics

Data were cleaned and summary statistics presented here are for *y* and *x*.
There were `r N.CASES` records.

## Summary Tables

Sometimes *numSummary* can produce problematic output for *knitr* but
really should be OK given it is used inside R Commander.

```{r, results='asis'}
## pander(RcmdrMisc::numSummary(clean_data)) # but stored summary so use that
pander(sumData$table)
```

This may be useful too:

```{r, results='asis'}
knitr::kable(psych::describe(clean_data), digit=1, caption = "Summary statistics")
```

## Summary Plots

A simple scatterplot.

```{r, echo=FALSE}

```

A ggplot2 plot

```{r, echo=FALSE, fig.cap = "Fitted line and smoothed fit"}
gg1
```
